A novel route to the spontaneous formation of porous crystals via viscoelastic phase separation

### 2015-11-20 crystal-gel/nature/crystal_gel2.tex

\begin{figure*}[!t]
 \centering
 \includegraphics[width=14cm]{figure2_n}
 % crystal_size.eps: 0x0 pixel, 300dpi, 0.00x0.00 cm, bb=(atend)
\caption{{\bf Percolated networks: {\bf a:} gel; {\bf b:} crystal-gel.} The gel state is obtained from the state
point $\phi\approx 0.30$ and $c_p=1.07$ mg/g, while the crystal-gel is obtained at the same $\phi$ but
at lower polymer concentration, $c_p=0.38$ mg/g. The top row shows depicts the networks as a continuous field that has
been obtained by applying a gaussian filter to the position of the particles (of width equal to the inter-particle distance) and
plotting the surface which bounds the highest 20\% values of the field. \textcolor{blue}{We can clearly see not only the percolated nature of both network, 
but also the difference in the smoothness of the network surface between amorphous and crystal gels.} 
The lower row depicts slabs of 5 particle diameter thickness,
with particles colored according to the following code: red (fcc), green (hcp), white (crystal surface particles), cyan (liquid particles), magenta (gas particles). 
\textcolor{blue}{We note that there remain a very few liquid particles and the network is almost crystalline.}} 
\label{fig:network}
\end{figure*}

>>>>

\begin{figure*}[!t]
 \centering
 \includegraphics[width=14cm]{figure2_n}
 % crystal_size.eps: 0x0 pixel, 300dpi, 0.00x0.00 cm, bb=(atend)
\caption{{\bf Percolated networks: {\bf a:} gel; {\bf b:} crystal-gel.} The gel state is obtained from the state
point $\phi\approx 0.30$ and $c_p=1.07$ mg/g, while the crystal-gel is obtained at the same $\phi$ but
at lower polymer concentration, $c_p=0.38$ mg/g. The top row shows depicts the networks as a continuous field that has
been obtained by applying a gaussian filter to the position of the particles (of width equal to the inter-particle distance) and
plotting the surface which bounds the highest 20\% values of the field. We can clearly see not only the percolated nature of both network, 
but also the difference in the smoothness of the network surface between amorphous and crystal gels. 
The lower row depicts slabs of 5 particle diameter thickness,
with particles colored according to the following code: red (fcc), green (hcp), white (crystal surface particles), cyan (liquid particles), magenta (gas particles). 
We note that very few liquid particles remain and the network is almost crystalline.} 
\label{fig:network}
\end{figure*}
